HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-10 scnn.tex
todo & typo

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item (TK) check text figure 1
	\item (TK) Related work in cosmo. The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}. Aren't there applications in cosmology for the other (c.f. related work section) approaches? Most of them are illustrated in omnidirectional imagery.
	\item (MD) distinction between CNN and FCN
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
    \item (TK) check if papers which appear as arxiv were not published in a conference or journal
    \item (TK) check part sphere notebook and whole sphere
    \item (TK) read everything
    \item (NP) Put Raphael in the dataset author. 
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (TK) color text in 2.8
    \item (NP) D.18 text size bigger
    \item (NP) Remove caption B.13
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item Check names: we use HealpixNet, HealpixNet variant CNN, HealpixNet variant FCN
    \item (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item Change equation after (2) and check all kroneker
	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
	\item Try to make the paper shorter?
	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
    \item (TK) fix the bibliography
    \item Check links in footnotes.

@@

Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
In that specific case, the filtering operation \eqnref{graph_convolution_fourier} becomes
\begin{equation} \label{eqn:graph_convolution_monomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
This operation is performed in the vertex domain.
The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values. The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch. In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch. Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
% \todo{Better vertex domain explanation.
% \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
% \TK{For me it's understandable:)}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{border_effects}
	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface. A filter is localized on pixel $i$ as $h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}). The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$. The filter is not isotropic anymore when localized on the left corner due to border effects. The graph representation of a manifold assumes reflective border conditions.}
	\label{fig:border_effects}
\end{figure}

>>>>

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item (TK) check text figure 1
	\item (TK) Related work in cosmo. The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}. Aren't there applications in cosmology for the other (c.f. related work section) approaches? Most of them are illustrated in omnidirectional imagery. If none, say it and mention some alternatives, e.g., wavelets?
	\item (MD) distinction between CNN and FCN
	\item (MD) check paragraph on our chosen architecture in the Experiments sections
    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
    \item (TK) check if papers which appear as arxiv were not published in a conference or journal
    \item (TK) check part sphere notebook and whole sphere
    \item (TK) read everything
    \item (NP) Put Raphael in the dataset author. 
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
	\item (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
    \item (NP) D.18 text size bigger
    \item (NP) Remove caption B.13
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
	\item Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
    \item (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
	\item (NP) Change equation after (2) and check all kroneker
	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
    \item (TK) fix the bibliography
    \item Check links in footnotes.

@@

Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
In that specific case, the filtering operation \eqnref{graph_convolution_fourier} becomes
\begin{equation} \label{eqn:graph_convolution_monomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
In our case, the Laplacian is extremely sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
This operation is performed in the vertex domain.
The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values. The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch. In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch. Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
% \todo{Better vertex domain explanation.
% \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
% \TK{For me it's understandable:)}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{border_effects}
	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface. A filter is localized on pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}). The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$. The filter is not isotropic anymore when localized on the left corner due to border effects. The graph representation of a manifold assumes reflective border conditions.}
	\label{fig:border_effects}
\end{figure}
